Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

Construct
\myeqn{
    H' &=& \{h' \mid h \in H \text{ and its trimmed segment $h'$ exists} \}. \nn
}
The construction requires solving an instance of Problem $\mathscr{C}$, which takes $O(n \log n)$ time based on the discussion in Section~\ref{sec:bricks}.

>>>>

Construct
\myeqn{
    H' &=& \{h' \mid h \in H \text{ and its trimmed segment $h'$ exists} \}. \nn
}
The construction requires solving an instance of Problem $\mathscr{C}$ (with $H$ and $R_{k-2}$ as the input), which takes $O(n \log n)$ time based on the discussion in Section~\ref{sec:bricks}.
